%%%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Change the font size of your document - 10pt, 12.1pt, etc.
\documentclass[letterpaper,11pt,oneside]{article}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
%\usepackage{hyperref}
\usepackage[hidelinks]{hyperref}
\usepackage{blindtext}
\usepackage{url}

\usepackage{enumitem}

\usepackage{blindtext}
\usepackage[normalem]{ulem}

\usepackage{gensymb}
\usepackage{amsfonts}
\usepackage{amsmath}

\usepackage{color}
\usepackage{booktabs}


\usepackage{graphicx}
\graphicspath{ {images/}} %upload your signature to this file
%Change the margins to fit your CV/resume content
\usepackage[left=1in, right=1in, bottom=1.25in, top=1.25in]{geometry}
\usepackage{kotex}
%Skype information - include your Skype name for a link to add you on Skype
%\newcommand*{\Skype}{\href{skype:john.smith?add}{john.smith}} 
%\newcommand{\Absender}[1][\normalsize]{\Skype} 

%Changes the page numbers - {arabic}=arabic numerals, {gobble}=no page numbers, {roman}=Roman numerals
\pagenumbering{gobble}

%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%% NAME OF APPLICANT %%%%%%%%%%%%%%%%%%%

\noindent  \LARGE{\textbf{Dowon Song}}  \\
\vspace{-2ex}
\normalsize
%%%%%%%%%%%%%%%%% CONTACT INFORMATION %%%%%%%%%%%%%%%%%
% Your email address, website, and Skype name are links to send email, open your website and add you on Skype. 

\begin{center}
\begin{tabular}{l l}
 Korea University    & \hspace{1in}
                       \href{mailto:dowon\_song@korea.ac.kr}{Email :
                       dowon\_song@korea.ac.kr} \\
 Software Analysis Laboratory  
 % & \hspace{1in} {Homepage : \url{prl.korea.ac.kr/\~minseok}}   \\
              %& \hspace{1in} Skype: \Absender  \\
 & \hspace{1in} Phone: +82 10-3105-0454 \\
\end{tabular}
\end{center}

\vspace{1em}

%%%%%%%%%%%%%%%%% MAIN BODY %%%%%%%%%%%%%%%%%%%%%%%%%%%
% The main body is contained in a tabular environment. To move sections onto the next page, simply end the tabular environment and begin a new tabular environment.

\noindent{\Large\bfseries Research Areas}\\[-0.5em]
\rule{\textwidth}{0.4pt}
My research focuses on automated software debugging by leveraging
program analysis and program synthesis.

\vspace{1.6em}
\noindent{\Large\bfseries Professional Experience}\\[-0.5em]
\rule{\textwidth}{0.4pt}
\renewcommand{\arraystretch}{1.2}
\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
Postdoctoral Researcher, \textbf{Software Analysis Laboratory, Korea University} 
& 2026.04 -- Present
\end{tabular*}
\renewcommand{\arraystretch}{1.0}

\vspace{1.6em}
\noindent{\Large\bfseries Educational Background}\\[-0.5em]
\rule{\textwidth}{0.4pt}
\renewcommand{\arraystretch}{1.2}
\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
Integrated M.S./Ph.D. in Computer Science, \textbf{Korea University} 
& 2018.03 -- 2026.02 \\
B.S. in Computer Science, \textbf{Korea University} 
& 2014.03 -- 2018.02
\end{tabular*}
\renewcommand{\arraystretch}{1.0}

\vspace{1.6em}
\noindent{\Large\bfseries Awards}\\[-0.5em]
\rule{\textwidth}{0.4pt}
\begin{enumerate}
  \item Outstanding Paper Award, Graduate School, Korea University, Aug 2021
  \item Second Prize, Undergraduate Research Competition, 
        Department of Computer Science, Korea University, May 2017
\end{enumerate}

\vspace{1.6em}
\noindent{\Large\bfseries Publications}\\[-0.5em]
\rule{\textwidth}{0.4pt}
Publications in top-tier conferences in programming languages and software engineering (OOPSLA 2025, FSE 2021, OOPSLA 2019, and OOPSLA 2018).
\begin{enumerate}    
    \item{\underline {\textbf{Dowon Song}} and 
      Hakjoo Oh. 
      \textsl{Enhancing APR with PRISM: A Semantic-Based Approach to Overfitting Patch Detection.} 
      \textbf{OOPSLA 2025}: ACM Conference on Object-Oriented Programming, Systems, Languages, and Applications}\\
    \item{\underline {\textbf{Dowon Song}}, Woosuk Lee, and 
      Hakjoo Oh. \textsl{Context-Aware and Data-Driven Feedback Generation for Programming Assignments.} \textbf{ESEC/FSE 2021}: ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering}\\
    \item{\underline {\textbf{Dowon Song}}, Myungho Lee, and 
      Hakjoo Oh. \textsl{Automatic and Scalable Detection of Logical Errors in Functional Programming Assignments.} \textbf{OOPSLA 2019}: ACM Conference on Object-Oriented Programming, Systems, Languages, and Applications}\\
    \item{Junho Lee, \underline{\textbf{Dowon Song}}, Sunbeom So, and
      Hakjoo Oh. \textsl{Automatic Diagnosis and Correction of Logical Errors for Functional Programming Assignments.} \textbf{OOPSLA 2018}: ACM Conference on Object-Oriented Programming, Systems, Languages, and Applications}\\
\end{enumerate}

\vspace{1.6em}
\noindent{\Large\bfseries Talks}\\[-0.5em]
\rule{\textwidth}{0.4pt}
\begin{enumerate}
  \item{Enhancing APR with PRISM: A Semantic-Based Approach to Overfitting Patch Detection. Paper presentation at OOPSLA 2025. Singapore. Oct 2025.}

  \item{PRISM: 자동 수정 기술 성능 향상을 위한
의미기반 과적합 패치 탐지. STAAR Summer Workshop. Seoul, Jul 2025.}
	
  \item{Context-Aware and Data-Driven Feedback Generation for Programming Assignments. STAAR Winter Workshop. Jeju, Feb 2022.}

  \item{Context-Aware and Data-Driven Feedback Generation for Programming Assignments. Paper presentation at FSE 2021. Online, Aug 2021.}
		
	\item{Automatic and Scalable Detection of Logical Errors in Functional Programming Assignments. Invited talk at KCC 2020. Online, Jul 2020.} 
  
	\item{Automatic and Scalable Detection of Logical Errors in Functional Programming Assignments. Paper presentation at OOPSLA 2019. Athens, Oct 2019.} 
	
  \item{Automatic Grading and Feedback Generation for Functional Programming Assignments. SIGPL Summer 2019. PyeongChang, Aug 2019.}
	
  \item{Automatic Diagnosis and Correction of Logical Errors for Functional Programming Assignments. Invited talk at KCSE 2019. PyeongChang, Jan 2019.}
  
	\item{Automatic Diagnosis and Correction of Logical Errors for Functional Programming Assignments. Invited talk at PLATEAU 2018. Boston, Nov 2018.}
	
	% \item{Poster Session, SIGPL Summer Workshop 2017. Chuncheon,
	% 	Korea.  August 2017.}
\end{enumerate}

\end{document}
